It's COMPAS-licated Can We Find Fairness in the COMPAS Risk Assessment Algorithm?

### 2022-03-07 Paper_Draft1/Draft1.tex
adding title, fixing authors formatting

%=================================================================
% Full title of the paper (Capitalized)
\Title{Full title of the paper (Capitalized)}

% Authors, for the paper (add full first names)
\Author{$^{}$}

% Authors, for metadata in PDF
\AuthorNames{}

@@

% Current address and/or shared authorship
\firstnote{Current address: Updated affiliation}
\secondnote{These authors contributed equally to this work.}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{x <-}\StringTok{ }\NormalTok{tibble}\OperatorTok{::}\KeywordTok{tribble}\NormalTok{(}\OperatorTok{~}\StringTok{`}\DataTypeTok{Title 1}\StringTok{`}\NormalTok{, }\OperatorTok{~}\StringTok{`}\DataTypeTok{Title 2}\StringTok{`}\NormalTok{, }\OperatorTok{~}\StringTok{`}\DataTypeTok{Title 3}\StringTok{`}\NormalTok{,}
\StringTok{"entry 1"}\NormalTok{, }\StringTok{"data"}\NormalTok{, }\StringTok{"data"}\NormalTok{,}
\StringTok{"entry 2"}\NormalTok{, }\StringTok{"data"}\NormalTok{, }\StringTok{"data"}
\NormalTok{)}

\NormalTok{knitr}\OperatorTok{::}\KeywordTok{kable}\NormalTok{(x, }\DataTypeTok{caption =} \StringTok{"This is a table caption. Tables should be placed in the main text near to the first time they are cited.}\CharTok{\textbackslash{}\textbackslash{}}\StringTok{label\{tab:mytable\}"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{longtable}[]{@{}lll@{}}
\caption{This is a table caption. Tables should be placed in the main
text near to the first time they are
cited.\label{tab:mytable}}\tabularnewline
\toprule
Title 1 & Title 2 & Title 3\tabularnewline
\midrule
\endfirsthead
\toprule
Title 1 & Title 2 & Title 3\tabularnewline
\midrule
\endhead
entry 1 & data & data\tabularnewline
entry 2 & data & data\tabularnewline
\bottomrule
\end{longtable}

>>>>

%=================================================================
% Full title of the paper (Capitalized)
\Title{It's COMPAS-licated Can We Find Fairness in the COMPAS Risk
Assessment Algorithm?}

% Authors, for the paper (add full first names)
\Author{Amrita Acharya$^{1, 2}$, Dianne Caravela$^{1, 3}$, Eunice
Kim$^{1, 4}$, Emma Kornberg$^{1, 5}$, Elisabeth Nesmith$^{1, 6}$}

% Authors, for metadata in PDF
\AuthorNames{Amrita Acharya, Dianne Caravela, Eunice Kim, Emma
Kornberg, Elisabeth Nesmith}

@@

% Current address and/or shared authorship

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{x }\OtherTok{\textless{}{-}}\NormalTok{ tibble}\SpecialCharTok{::}\FunctionTok{tribble}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\StringTok{\textasciigrave{}}\AttributeTok{Title 1}\StringTok{\textasciigrave{}}\NormalTok{, }\SpecialCharTok{\textasciitilde{}}\StringTok{\textasciigrave{}}\AttributeTok{Title 2}\StringTok{\textasciigrave{}}\NormalTok{, }\SpecialCharTok{\textasciitilde{}}\StringTok{\textasciigrave{}}\AttributeTok{Title 3}\StringTok{\textasciigrave{}}\NormalTok{,}
\StringTok{"entry 1"}\NormalTok{, }\StringTok{"data"}\NormalTok{, }\StringTok{"data"}\NormalTok{,}
\StringTok{"entry 2"}\NormalTok{, }\StringTok{"data"}\NormalTok{, }\StringTok{"data"}
\NormalTok{)}

\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(x, }\AttributeTok{caption =} \StringTok{"This is a table caption. Tables should be placed in the main text near to the first time they are cited.}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{label\{tab:mytable\}"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{longtable}[]{@{}lll@{}}
\caption{This is a table caption. Tables should be placed in the main
text near to the first time they are
cited.\label{tab:mytable}}\tabularnewline
\toprule
Title 1 & Title 2 & Title 3 \\
\midrule
\endfirsthead
\toprule
Title 1 & Title 2 & Title 3 \\
\midrule
\endhead
entry 1 & data & data \\
entry 2 & data & data \\
\bottomrule
\end{longtable}
